Universal Anonymous Signatures

### 2022-06-13 prism-backend/research/gsac/app-model-related.tex
Defining DAC.

We adopt the model in \cite{fhs19}, where security of anonymous credentials
(with selective disclosure). Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ and $UserKeyGen$ algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol is equivalent to
the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \cite{fig:model-ac}, with inocuous adaptations to
make them more suitable for comparison with our definitions.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        (\opk,\osk) \gets OrgKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,D) \rangle \\
        \pcif b = 1 \land \forall j: \OWNR[j] \in \CU
        \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk',\osk') \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk')$.
\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with $\opk'$ from \parm as opener public key.
\end{description}

@@

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~ wins its game. Note that, since $b=1$ in line 4 of the
  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
  also returns $1$ in the sign unforgeability game of \UAS. In addition, if
  there is no corrupt user with a credential containing $D$, then this leads to
  \advB winning at line 8 in \figref{fig:exp-uas-unfor-sign}, as no credential
  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
  function output $\yeval=D$. Thus, \advB wins with the same probability as
  \adv~ does.  
  %
  \qed
\end{proof}

@@

We give a simple definition for delegatable anonymous credentials extending
the anonymous credential model in \cite{fhs19}. Next, we briefly describe a
construction based on $(\fissue^n,\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
show that it satisfies our basic notion of delegatable anonymous credentials.
Roughly, a delegatable anonymous credential scheme is an anononymous credential
scheme in which every issuer of level $n$ can only issue credentials of level
$n+1$. For simplicity, we restrict to the case of using only one credential per
signature, but the generalization is trivial. Note that, in addition to the
algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
which, given an issuer's public key and its alleged level, returns $1$ if the
level is correct, or $0$ otherwise.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,dac}(1^\secpar)$}{%
        b^* \gets \adv^{HU,CU,obtain,Show,LoR} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\        
        (D,n+1,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
        D \cup \lbrace n+1 \rbrace)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
        \not\subseteq \ATTR[j])~\lor\\
        \pcind level(\opk,n) = 0: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. \OWNR and \ATTR tables are essentially as
    in \secref{ssec:model-uas}. $level(\opk,n)$ is a helper function that
    returns the $1$ if the level of \opk is $n$, or $0$ otherwise.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
We adopt the simplification that the level of an issuer is encoded in its public
key, and anybody can check the issuer's level via some publicly accessible
mechanism. This can be ensured, e.g., by having each issuer post its
  public key along with a proof of ownership of a level $n$ credential -- which
  can be trivially done in \CUASGen.

@@

Given $level$, the security proofs are as for \CUASAC, with the addition that,
in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
can be directly used to break the sign unforgeability property of the underlying
\CUASGen scheme.

>>>>

We adopt the model in \cite{fhs19}, where security of anonymous credentials
(with selective disclosure). Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol is equivalent to
the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \cite{fig:model-ac}, with inocuous adaptations to
make them more suitable for comparison with our definitions.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\parm) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets IssKeyGen(\parm) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,D) \rangle \\
        \pcif b = 1 \land \forall j: \OWNR[j] \in \CU
        \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk')$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with $\opk'$ from \parm as opener public key.
\end{description}

@@

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~ wins its game. Note that, since $b=1$ in line 5 of the
  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
  also returns $1$ in the sign unforgeability game of \UAS. In addition, if
  there is no corrupt user with a credential containing $D$, then this leads to
  \advB winning at line 9 in \figref{fig:exp-uas-unfor-sign}, as no credential
  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
  function output $\yeval^0=D$. Thus, \advB wins with the same probability as
  \adv~ does.  
  %
  \qed
\end{proof}

@@

\todo{Rewrite when the full rewriting of the paper is done. For now, just
  adapting the construction.}
We give a simple definition for delegatable anonymous credentials extending
the anonymous credential model in \cite{fhs19}, but drawing inspiration from
\cite{bcc+09}. Next, we briefly describe a construction based on $(\fissue^n,
\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
show that it satisfies our basic notion of delegatable anonymous credentials.
Roughly, a delegatable anonymous credential scheme is an anononymous credential
scheme in which every issuer of level $n$ can only issue credentials of level
$n+1$. For simplicity, we restrict to the case of using only one credential per
signature, but the generalization is trivial. Note that, in addition to the
algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
which, given an issuer's public key and its alleged level, returns $1$ if the
level is correct, or $0$ otherwise.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }
      \vspace*{0.5em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\        
        (D,n+1,\st) \gets \adv^{\mathcal{O}_{forge}}(\parm,\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
        D \cup \lbrace n+1 \rbrace)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
        \not\subseteq \ATTR[j])~\lor\\
        \pcind level(\opk,n) = 0: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,Obtain,Issue,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets \lbrace
    HU,CU,Obtain,Issue,Show,SigLoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace
    HU,CU,ObtIss,Issue,Show \rbrace$. $IssLor$ is equivalent to \OBTCHALb in
    \UAS, whereas $SigLor$ is equivalent to \CHALb. Also, \OWNR and \ATTR
    tables are essentially as in \secref{ssec:model-uas}.
    $level(\opk,n)$ is a helper function that returns the $1$ if the level of
    \opk is $n$, or $0$ otherwise.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
In a nutshell, we distinguish between top-level issuers, and users who delegate
their credentials, thus acting as lower-level issuers. Top-level issuers are
exactly as issuers in \CUASGen. Lower-level issuers need to make public an
issuance public key that reveals the attributes they are willing to delegate,
and their credential level. The issuance function has to prove that the
requestor is asking
for a credential that: (1) increments the credential level exactly by one, and
(2) the requested attributes are a subset of those that the low-level issuer
can delegate. Note that both conditions apply recursively. To prevent
mix-and-match attacks, in each (lower-level) credential we include as attributes
a ``serial number'' of the immediately upper level credential, and another one
for the credential being issued (\todo{see figure}). For a credential of
level $n$, the evaluation function must output a chain of proofs of knowledge of
a sequence of credentials of levels $n$ up to $1$, with matching serial number
pairs.

More concretely, we define issuance functions for low-level issuers to have
the following structure:

\begin{align}
  & \fissue^{n,r_n,\attrs}(\usk,\scred,\attrs') \coloneqq \lbrace
    \pcif \attrs'_1 = n+1 \land \attrs'_2 = r_n \land
    \attrs'_{[4..t]} \subseteq \attrs: \pcreturn 1; \pcelse \pcreturn 0
    \rbrace \nonumber \\
  &  \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace \textrm{Parse \cred
    as }(\cred',\Sig,r); \pi \gets K(\cred') \rbrace
\end{align}
\todo{XXXX}

Where $n$ is its depth in the delegation chain, $\attrs'_3$ must be some serial
number chosen by the issuer for the new credential, and $r_n$ is a random number
serving as serial number for the issuer's credential (chosen by its parent
issuer), and \attrs is the attribute set that it can delegate. Note that this
issuance funcion expects the first attribute of the requested credential to
encode the credential depth, the second attribute to encode the serial number
of the issuer's credential, and the third attribute to encode the random
number (chosen uniformly by the issuer) that will serve as identifier of the
produced credential. All other attributes only need to meet the condition of
being contained in the attributes \attrs of the issuer's credential.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If the issuer is a top-level
  issuer, $IssKeyGen$ simply runs \IKeyGen in \CUASAC. If it is a lower-level
  issuer (say, of level $n>1$), this is in fact a user, who has already run
  $UserKeyGen$ below (and thus, \IKeyGen), and owns a credential  over
  attributes \attrs, issued by some higher-level issuer. Thus, instead of
  running \SBCMKeyGen, sets $\isk \gets \usk$, and its issuance function to
  $\fissue^{n,r_n,\attrs}$. % The
  % lower-level issuer also runs $(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  % \feval^{\dattrs})$, where $\feval^{\dattrs}$ is as defined as in
  % \appref{sapp:related-models-ac}, and thus reveals the attributes that the
  % low-level issuer can delegate. That is, by definition of $\feval^{\dattrs}$,
  % given the \attrs defined in $\fissue^{n,r_n,\attrs}$, $\yeval = \attrs$ (also,
  % note that the issuer's credential may contain other non-delegatable
  % attributes).
  Finally, the lower-level issuer sets $\ipk \gets (\ipk,n,r_n,\attrs,
  \fissue^{n,r_n,\attrs})$.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
  $\usk \gets \isk$.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  We assume that the set \attrs of attributes to be included in the credential
  are of the form $(n+1,r_n,r_{n+1},\attrs')$, where $n+1$ is the level of the
  credential to be issued, $r_n$ is the identifier of the issuer's credential
  (or some special fixed value if it is a top level credential), $r_{n+1}$ is
  a serial number for the new credential, chosen by the issuer, and $\attrs'$
  is the attributes being requested by the user. Both issuer and user agree on
  these values beforehand. If the issuer is top-level, this protocol runs as in
  \CUASAC, for \attrs as above. Else, if the issuer is not top-level (say, it
  has level $n>1$), the protocol in \CUASAC is augmented as follows:

  \begin{itemize}
  \item \uline{User}: $r \gets \bin^l$ (for some appropriate $l$).
  \item \uline{User,Issuer}: Run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
    for \attrs as specified above.
  \item \uline{Issuer}: $\Sig=(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
    \feval^{n,\dattrs})$. Where \cred is the issuer's $n$-th level credential,
    and $\feval^{n,\dattrs}$ is as in \appref{sapp:related-models-ac}, plus
    revealing the credential level (encoded in \cred's first attribute).
  \item \uline{User}: Accept if $\Verify(\opk,\ipk,\Sig,r,\feval^{n,\dattrs})=
    1$, and return $(\cred,\ipk,\Sig,r)$ as $(n+1)$-level credential, where
    \cred is the credential produced in the interactive protocol at step 2.
    Otherwise, reject.
  \end{itemize}

  Note that, basically, the issuer proves that it owns a credential of level $n$
  over the attributes it is delegating.

\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  As in \CUASAC, but using $\feval^{n,\dattrs}$ as signature evaluation
  function.
\end{description}

\iffalse
We adopt the simplification that the level of an issuer is encoded in its public
key, and anybody can check the issuer's level via some publicly accessible
mechanism. This can be ensured, e.g., by having each issuer post its
  public key along with a proof of ownership of a level $n$ credential -- which
  can be trivially done in \CUASGen.

@@

Given $level$, the security proofs are as for \CUASAC, with the addition that,
in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
can be directly used to break the sign unforgeability property of the underlying
\CUASGen scheme.
\fi

### 2022-06-13 prism-backend/research/gsac/security-uas.tex
Defining DAC.

  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
  adversarial issuer are of
  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\crs_{\Issue},(\UK[\cuid_0],
  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\CCom,\attrs,\PUBIK[\cscid_0]))$. The
  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
  and \Sign). That is, the proofs for credential requests are generated as
  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\crs_{\Issue},\tau,(\CCom,\attrs,
  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.

  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
  Concretely, for the case of the proofs at issuance time, they are of the
  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\crs_{\Issue},\tau,(\CCom,\attrs,
  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
  by definition of the \OBTCHAL oracle. Hence, the produced proofs are exactly
  the same independently on the value of the bit $b$.

>>>>

  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
  adversarial issuer are of
  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\UK[\cuid_0],
  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\Ccom,\attrs,\PUBIK[\cscid_0]))$. The
  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
  and \Sign). That is, the proofs for credential requests are generated as
  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.

  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
  Concretely, for the case of the proofs at issuance time, they are of the
  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
  by definition of the \OBTCHALb oracle. Hence, the produced proofs are exactly
  the same independently on the value of the bit $b$.
